%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% David Pietrocola - Resume
%
% Original author of the template:
% Debarghya Das (http://debarghyadas.com)
%
% Template modified by:
% David Pietrocola (https://davidpietrocola.com)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{DavidPietrocola-resume}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LAST UPDATED DATE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{David}{Pietrocola}{ \urlstyle{same}

Toronto, ON\\
    +1 (xxx)-xxx-xxxx |
    \href{mailto:pietrocoladavid@gmail.com}{pietrocoladavid@gmail.com} | \href{http://davidpietrocola.com}{davidpietrocola.com} }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN ONE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.37\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Advanced Diploma in}
\subsection{Software Engineering}
\descript{Centennial College}
\location{Jan 2022 - Dec 2024 | Toronto, ON}

{\bf Relevant Coursework:} Advanced Database \\ DSA \textbullet{} Software Testing \textbullet{} Unix/Linux OS \\ Web Application Programming\\
\location{ Cum. GPA: 4.3 / 4.5 }
%italics
{\bf Award:} \textit{Global Perspective Digital Badge}\\for excellence in engagement within\\leadership and volunteer activities. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Technical Skills}
\smallsep
\location{Proficient with:}
\smallsep
Java \textbullet{}
JavaScript (ES6) \textbullet{} TypeScript\\   SQL \textbullet{} OOP Concepts
% Python 3 \textbullet{} C\#\  \textbullet{}
\mediumsep \\
\location{Frameworks and Libraries:}
\smallsep
Next.js\textbullet{}Express.js \textbullet{} Node.js \textbullet{} React
% .NET \textbullet{} 
\mediumsep \\
\location{Tools:}
\smallsep
AWS RDS \textbullet {} AWS Lambda \\CloudFormation \textbullet{}
Git \textbullet{} GitHub \\ Postman \textbullet{} Jira \textbullet {}Azure \textbullet{} Docker \textbullet{} Jenkins \\Swagger UI \textbullet{}MongoDB \textbullet{} PostgreSQL
\sectionsep
\subsection{Soft Skills}
\smallsep 
Effective organization skills\\Communication abilities in multiple languages, including English, Italian, and Russian
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     HACKATHONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Hackathons}
\begin{tabular}{rll}
Apr 2023& \bf{1\textsuperscript{st}/79} & \href{https://devpost.com/software/tbd-p9xqhv}{MapHacks 2}\\
Apr 2023&\bf{4\textsuperscript{th}/675} & \href{https://devpost.com/software/hackthefeed-1ycujf}{EducateHack}\\
Apr 2023& \bf{1\textsuperscript{st}}& \href{https://devpost.com/software/tba-z5dkvc}{DeerHacks}\\
May 2023 & \bf{1\textsuperscript{st}}& \href{https://devpost.com/software/tba-asjk6y}{MetHacks}\\
Sep 2023 && Hack The North\\
Oct 2023  & \bf{Hon. Men.}& \href{https://www.spaceappschallenge.org/2023/find-a-team/intergalactic-pirates/}{NASA Space App}\\
Oct 2023 && \href{https://devpost.com/software/dataplace}{HarvardHack}\\
\end{tabular}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications \&\ Clubs}
\begin{tabular}{lr}
Dec 2022&  \textbf{\underline{\href{https://certificates.cs50.io/5c64e9de-6da5-43d2-8e2d-f888535489b7.pdf?size=letter}{CS50 - HarvardX}}}  \\
 Apr 2023& \textbf{\underline{\href{https://www.credly.com/badges/94d2934f-5383-4e1c-a55e-47515c806f7f/linked_in_profile}{Cloud Practitioner - AWS}}}\\
 July 2023& \textbf{\underline{\href{https://www.credly.com/badges/21d50060-794b-4d25-b926-20b19de12ebe/linked_in_profile}{MongoDB Assoc Developer}}}\\
Current & Centennial Programming Club\\
Current & Google Developer Club - UofT

\end{tabular}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links}
LinkedIn://  \href{https://www.linkedin.com/in/pietrocoladavid/}{\bf pietrocoladavid} \\
Github:// \href{https://github.com/DavDeDev}{\bf DavDeDev} \\

% Devpost://  \href{https://devpost.com/DavDeDev?ref_content=user-portfolio&ref_feature=portfolio&ref_medium=global-nav}{\bf DavDeDev} \\
% Hackerrank://  \href{https://devpost.com/DavDeDev?ref_content=user-portfolio&ref_feature=portfolio&ref_medium=global-nav}{\bf DavDeDev}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.62\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Professional Experience}

% \runsubsection{Full Stack Developer}
% \descript{| TD Bank}
% \location{Anticipated start date May 2024 | Toronto, ON}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space


\runsubsection{Backend Developer}
\descript{| Omers}
\location{Sep 2023 - Present | Toronto, ON}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developing new microservices in {\bf Java Spring Boot} as a part of the Calculations team to accurately compute Pensions and Contributions for {\bf thousands} of employees.
\item Spearheaded a comprehensive overhaul of the existing microservice, leveraging {\bf Generics} to enhance code {\bf abstraction}, resulting in a more efficient and scalable system.
\item Gaining expertise in best practices for {\bf testing} and {\bf deploying} new changes to ensure the reliability and stability of the software.
\item Gained in-depth knowledge of {\bf design patterns'} applications, and enterprise-level {\bf cloud} infrastructure.
\end{tightemize}

\vspace{\topsep} 


\runsubsection{Backend Developer}
\descript{| Wimtach}
\location{Jan 2023 - Aug 2023 | Toronto, ON}
\begin{tightemize}
\item Designed and deployed an {\bf MS SQL server database} on {\bf AWS RDS} and managed the ongoing performance and security of the database, implementing proactive monitoring and optimization strategies using AWS CloudWatch and AWS Budget.
\item Developed APIs in Python, adopted a {\bf serverless architecture} using {\bf AWS Lambda Functions} and {\bf API Gateway} for scalability and cost efficiency.
\item  Manage {\bf DevOps} practices and supported the {\bf AWS infrastructure}, ensuring {\bf99.9\%\ uptime} and a {\bf40\%\ reduction in deployment time}.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TECHNICAL PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

% \runsubsection{MintBuddy - Chat Bot}
% \descript{| \href{https://github.com/WilliamUW/MintBuddy}{ Github} }
% \location{Apr 2023 | Deerhacks \textbullet{} Toronto, ON}
% \begin{tightemize}
% \item Developed a chatbot utilizing {\bf Voiceflow} (leveraging GPT 3.5 and \\GPT 4.0), Verbwire APIs, and Stablediffusion API to enable users to mint new {\bf NFTs on-chain}.
% \item Built and maintained a robust {\bf CI/CD pipeline} using AWS and GitHub Actions to continuously deploy the chatbot to S3, ensuring a reliable and seamless user experience while also minimizing downtime. 
% \end{tightemize}
% \sectionsep

\runsubsection{Opzione Zen}
\descript{| \href{https://chrome.google.com/webstore/detail/opzione-zen/pbkpdonipildmhpcpdjegimbhnkogpfi}{ Extension},\href{https://github.com/DavDeDev/Opzione-Zen}{ Github} }
\location{Fall 2022 | HarvardX \textbullet{} Toronto, ON}
\begin{tightemize}
\item Built a Chrome extension that activates a reading mode in websites: W3School, MDN, Google Dev, Stack Overflow using JavaScript and CSS.
\item Utilized the latest Chrome {\bf extension API} (Manifest V3) version to access browser features and interact with web pages.
\end{tightemize}
\sectionsep

% \runsubsection{Jobs search - RESTful API}
% \descript{| \href{https://seal-app-njg7y.ondigitalocean.app/}{ Website},\href{https://github.com/DavDeDev/JOBs-API}{ Github} }
% \location{Fall 2022 | Toronto, ON}
% \begin{tightemize}
% \item Built a job search API using {\bf Node.js} and {\bf Express} framework.
% \item Utilized  {\bf MongoDB} to store data and  {\bf CRUD} operations.
% \item Tested and debugged the API with Postman and integrated it with front-end documentation using SwaggerUI and Apimatic.
% \end{tightemize}
% \sectionsep

\runsubsection{DisCal - Discord Bot}\descript{|  \href{https://discord.gg/8JteNuBzvG}{ Live}, \href{https://github.com/DavDeDev/DisCal}{Github}, \href{https://app.codesee.io/maps/public/94cb8890-2cba-11ee-bc2e-37ecf848c013}{Codesee} }
\location{Summer 2023 | Toronto, ON}
\begin{tightemize}
\item Developed a Discord bot using {\bf TypeScript}, Discord.js and {\bf Google APIs} that allows server's users to manage a shared Google Calendar and collect all the upcoming Hackathons, conferences and other events from Discord.
\item Setup a CI/CD pipeline using {\bf AWS CodeDeploy} and {\bf EC2} instance.
\end{tightemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Research}
% \runsubsection{WIMTACH}
% \descript{| Researcher}
% \location{Jan 2023 - May 2023 | Toronto, ON}
% Conducted performance testing and identified areas for optimization in a business project.
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RELEVANT EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Relevant Experience}
\runsubsection{Mentor}
\descript{| Centennial College }
\location{April 2023 – present | Toronto}
\begin{tightemize}
\item Mentored 7 incoming college students, providing guidance, support, and resources to help them successfully transition to college. Demonstrated strong {\bf leadership skills} in the mentorship role, inspiring and motivating mentees to achieve their academic and personal goals.
\item Provided ongoing coaching and support to mentees, helping them develop essential skills and succeed inside and outside the classroom.
\end{tightemize}
\end{minipage} 

\end{document}  \documentclass[]{article}